Papers

### 2023-01-17 quarto/index.qmd
update

**Aston Zhang** is a senior scientist at Amazon Web Services AI Research.
He focuses on efficient and robust methods for machine learning and natural language processing.
He received the <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award (2021)</a>,
the ACM Ubicomp Distinguished Paper Award (2018), and the ACM SenSys Best Paper Award Nomination (2017).
His <a href="https://github.com/d2l-ai" target="_blank">open-source</a> textbook,
<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a>,
has been <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
He obtained his Ph.D. in Computer Science from University of Illinois at Urbana-Champaign.

@@

Hi! I'm happy to connect and discuss. Preferred mode of contact is my email.
My team is hiring intern scientists in machine learning
(at our <a href="https://www.google.com/maps/place/2795+Augustine+Dr,+Santa+Clara,+CA+95054/@37.3835062,-121.9778599,17z/data=!3m1!4b1!4m5!3m4!1s0x808fc9f208b94da1:0xd2df9ae053c51af0!8m2!3d37.383502!4d-121.9756659" target="_blank">Santa Clara office</a> or other global offices). Just drop me a line.

@@

For prospective 2023 interns: my team is hiring research interns in NLP or ML. Just email me.

>>>>

**Aston Zhang** is a senior scientist at Amazon Web Services AI Research.
He studies efficient and robust methods for machine learning and natural language processing, currently focusing on large language models.
He received the <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award (2021)</a>,
the ACM Ubicomp Distinguished Paper Award (2018), and the ACM SenSys Best Paper Award Nomination (2017).
His <a href="https://github.com/d2l-ai" target="_blank">open-source</a> textbook,
<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a>,
has been <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
He obtained his Ph.D. in Computer Science from University of Illinois at Urbana-Champaign.

@@

Hi! I'm happy to connect and discuss.
My team is hiring intern scientists
at our <a href="https://www.google.com/maps/place/2795+Augustine+Dr,+Santa+Clara,+CA+95054/@37.3835062,-121.9778599,17z/data=!3m1!4b1!4m5!3m4!1s0x808fc9f208b94da1:0xd2df9ae053c51af0!8m2!3d37.383502!4d-121.9756659" target="_blank">Santa Clara office</a> or other global offices. Just email me.

@@
